---
title       : Predict weight based on height
subtitle    : A simplified use case to illustrate how to use slidify
author      : baohuiz
job         : statistician
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## A Web Application to Predict Your Weight

<iframe src='https://baohuiz.shinyapps.io/shinyapp/' width="500" height="300"></iframe>

--- .class #id 

## The regression model

The model weight ~ height is a simplified regression model just for illustration purpose:


```
   weightByHeightModel <- function(height) 40 + 1.6 * height
```

---

## Let's look at some examples

If I am 60 inches tall:

```{r, echo=TRUE}
   weightByHeightModel <- function(height) 40 + 1.6 * height
   height1 <- 60
   weight1 <- weightByHeightModel(height1)
```
So I am `r weight1` lbs. 

If I am 70 inches tall:
```{r, echo=TRUE}
   weightByHeightModel <- function(height) 40 + 1.6 * height
   height2 <- 70
   weight2 <- weightByHeightModel(height2)
```
So I am `r weight2` lbs.

---

## Conclusions:

1. Obviously, the prediction function for weight based on height should be more sophisticated than presented here
2. For more accurate prediction, it may need to consider our varibles such as gender, age, race, etc.
3. But solidify is so impressive for building a data product.
